Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-27 paper/paper-arxiv.tex
organizing paper versions

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 6, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 27, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

### 2023-04-27 paper/paper-nature.tex
organizing paper versions

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

\hypertarget{next-steps}{%
\section{Next Steps}\label{next-steps}}

While our database makes a substantial contribution to the field, there
are a few areas for future development.

One important contribution would be to take advantage of similar records
that exist for the Senate over this same period and add them to our
database. The main challenge of this would be accounting for different
parliamentarians, but the broad structures would be similar, making many
elements of our code and methodology applicable to this work.

Earlier House of Representatives records also exist, and would be
valuable to include in future versions of our database. In some cases
however it is difficult to get XML records for certain dates, and the
earlier decades would require more cleaning and likely additional script
development to account for changes in structural formatting.

Having completed this work, we recognize components of our scripts which
could be developed in a more computationally efficient manner such as
our approach to splitting interjections and filling in MP details. In
future, it would be beneficial to review our methodological approach to
these steps, and consider approaches which are more concise where
appropriate.

Finally, Hansard records contain a number of statements throughout that
were not explicitly spoken in parliament. For example, the text in
Figure~\ref{fig-content_ex} beneath the bold subtitle ``Report from
Federation Chamber'' is not attributed to a particular MP and was not
spoken aloud during the parliamentary proceedings. In contrast, the text
which comes afterward was spoken aloud in parliament by the Speaker at
14:01. Generally, unspoken text is nested under
\texttt{\textless{}debate.text\textgreater{}} or
\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
text is categorized under \texttt{\textless{}speech\textgreater{}}.
Importantly, in our work we focus primarily on parsing spoken speech
content (i.e.~what is nested within
\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
by the Speaker in Figure~\ref{fig-content_ex}. For this reason, many
Hansard transcriptions which are not spoken text may not be captured in
our database. In future work, capturing this unspoken content in our
database would be a priority.

{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}

\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
for Hansard on 26 March 2013}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@
